Declarative Data Analytic

### 2015-05-27 paper.tex
Add meeting summary

\begin{itemize}
\item Tutorial finished: I have tried the example TCP records on the \saf
  website, and generated the traces that satisfy the three-way-handshake
  behavior.
\item Trying \saf on real-data now...
\end{itemize}

@@

>>>>

\paragraph{Progress.}

\begin{itemize}
\item Tutorial finished: I have tried the example TCP records on the \saf
  website, and generated the traces that satisfy the three-way-handshake
  behavior.
\item Trying \saf on real-data now... (Detailed information of the data is in
  the email).
\end{itemize}

\paragraph{Questions:}

@@

\section{Project}
\label{sec:project}

\subsection{Goal}
\label{sec:proj:goal}
% Help the user to define failure models of systems, so that the failure model
% could help identify the root cause of anomalies.

Develop a declarative language that allows the user to specify/query the root
cause of a system anomaly, so that the user does not need to handle low-level
logging data directly.

\section{Meeting Log}
\label{sec:meetlog}

\subsection{5/27}

We discussed about the skeleton of the project. The problem is much clearer
after the meeting. The goal of the project, at this stage, is to develop a
declarative language that helps a network administrator to specify/query the root cause of a
system problem, given overwhelming log information.

\paragraph{Questions}

\begin{itemize}
\item What are the current status of network diagnosis?
\item What is a good abstraction of root cause analysis?
\end{itemize}

\section{Reading List}
\label{sec:read}

Troubleshooting Blackbox SDN Control Software with Minimal Causal
Sequences. (link: http://www.eecs.berkeley.edu/~rcs/research/sts.pdf)

Fault Management in Distributed Systems. (link:
http://repository.upenn.edu/cgi/viewcontent.cgi?article=1960&context=cis_reports)
